---
output: md_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# hybridProcess

The goal of hybridProcess is to provide functions for fitting and simulation of hybrid processes, one kind of non-homogeneous Poisson processes (NHPP). Specifically, the intensity of this kind of NHPP is proportional to the product of a power term, and an exponential term, of time.

## Installation

You can install hybridProcess from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("clement-lee/hybridProcess")
```

## Example

Here is an example of simulating from, and fitting, a hybrid process, with power parameter $\lambda=0.66$, exponent $\theta = 0.1$, and scale parameter $\phi = 5.0$.

```{r load, echo = FALSE, include = FALSE, message = FALSE, error = FALSE, warning = FALSE, eval = TRUE}
library(hybridProcess)
```

```{r example}
# library(hybridProcess)
## Simulation
set.seed(1234L)
x <- sim_hybrid(
  T = 1000, x = 0.0, beta = 0.0, kappa = 0.0,
  lambda = 0.66, phi = 5.0, theta = 0.1,
  psi = 0.0, tau = Inf
)
## Fitting
obj0 <- optim(c(0.1, 0.1, 0.1), llik_nhpp_hybrid, x = x, control = optimctrl())
obj0$par # compare with true parameter values
```

## Further information
The example above uses a function `sim_hybrid()` that is more flexible than a simple hybrid process. A wrapper function `sim_wrapper()` enables simulation of a collection of hybrid processes, each of which can be initiated at a different time point, with the possible inclusion of a covariate. Such data can be fitted by a hierarchical model of hybrid processes, via the function `run_mcmc()`.

For details of the hierarchical model, as well as the definitions of other parameters in `sim_hybrid()`, please refer to [this ArXiv paper](https://arxiv.org/abs/1802.01987).